--- 
title: "A Mega-Analysis of Personality Predictions: Robustness and Boundary Conditions"
author: "Emorie D. Beck"
institution: "Washington University in St. Louis"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
delete_merged_file: false
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
editor_options: 
  chunk_output_type: console
---

# Workspace  
## Packages  

```{r, echo = F}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, error = F)
options(knitr.kable.NA = '')
```


```{r, echo = F}
load_url <- function (url, ..., sha1 = NULL) {
  # based very closely on code for devtools::source_url
  stopifnot(is.character(url), length(url) == 1)
  temp_file <- tempfile()
  on.exit(unlink(temp_file))
  request <- httr::GET(url)
  httr::stop_for_status(request)
  writeBin(httr::content(request, type = "raw"), temp_file)
  file_sha1 <- digest::digest(file = temp_file, algo = "sha1")
  if (is.null(sha1)) {
    message("SHA-1 hash of file is ", file_sha1)
  }
  else {
    if (nchar(sha1) < 6) {
      stop("Supplied SHA-1 hash is too short (must be at least 6 characters)")
    }
    file_sha1 <- substr(file_sha1, 1, nchar(sha1))
    if (!identical(file_sha1, sha1)) {
      stop("SHA-1 hash of downloaded file (", file_sha1, 
           ")\n  does not match expected value (", sha1, 
           ")", call. = FALSE)
    }
  }
  load(temp_file, envir = .GlobalEnv)
}

```


```{r packages}
library(knitr)
library(kableExtra)
library(readxl)
library(psych)
library(brms)
library(mice)
library(fixest)
library(parallel)
library(MuMIn)
library(MatchIt)
library(haven)
library(broom.mixed)
library(rstan)
library(tidybayes)
library(shiny)
library(plyr)
library(tidyverse)
library(furrr)
```


## Directory Path  
```{r path}
res_path <- "https://github.com/emoriebeck/selection/blob/master"
wd <- "/Volumes/Emorie Beck/projects/selection"
```

## Codebook  
Each study has a separate codebook indexing matching, covariate, personality, and outcome variables. Moreover, these codebooks contain information about the original scale of the variable, any recoding of the variable (including binarizing outcomes, changing the scale, and removing missing data), reverse coding of scale variables, categories, etc.  
```{r codebook}
# list of all codebook sheets
sheets <- sprintf("%s/codebooks/master_codebook_01.24.20.xlsx", wd) %>% excel_sheets()

# function for reading in sheets
read_fun <- function(x){
  sprintf("%s/codebooks/master_codebook_01.24.20.xlsx", wd) %>% read_xlsx(., sheet = x)
}

# read in sheets and index source
codebook <- tibble(
  study = sheets,
  codebook = map(study, read_fun)
)

## short and long versions of names of all categories for later use
studies <- c("addhealth", "bhps", "gsoep", "hilda", "hrs", "liss", "midus", "nlsy", "shp", "wls")
studies_long <- c("Add Health", "BHPS", "GSOEP", "HILDA", "HRS", "LISS", "MIDUS", "NLSY", "SHP", "WLS")

traits <- codebook$codebook[[2]] %>% filter(category == "pers") %>% 
  select(long_name = Construct, short_name = name)

outcomes <- codebook$codebook[[2]] %>% filter(category == "out") %>%
  select(long_name = Construct, short_name = name)

moderators <- codebook$codebook[[2]] %>% filter(category == "mod") %>%
  select(long_name = Construct, short_name = name, breaks, mod, mod_name)
```


## Other Supporting Documents  
```{r other docs}
# used personality waves 
p_waves <- sprintf("%s/codebooks/personality_waves.xlsx", wd) %>% read_xlsx()
# used covariates for specifications 
specifications <- sprintf("%s/codebooks/specifications.xlsx", wd) %>% read_xlsx()
# coded specificatoin curve results
spec_summ <- sprintf("%s/results/sca/SCA_summary.xlsx", wd) %>% read_xlsx()

# occupation code converters 
occ90to00 <- sprintf("%s/codebooks/occ_90-00.xls", wd) %>% read_xls() %>% mutate_at(vars(OCC90, OCC00), as.numeric)
occ70to90 <- sprintf("%s/codebooks/occ1970_occ1990dd.dta", wd) %>% read_dta() %>%
  setNames(c("OCC70", "OCC90"))
occ80to90 <- sprintf("%s/codebooks/occ1980_occ1990dd.dta", wd) %>% read_dta() %>%
  setNames(c("OCC80", "OCC90"))

# npb codes for ses
npb <- sprintf("%s/codebooks/npb.xlsx", wd) %>% read_xlsx() %>% 
  setNames(c("OCC00", "NPB", "desc"))
```


```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```
